Monte Carlo and bootstrap for all parameters

### 2024-08-06 MC_all.Rmd
Ready to knit with BCa

In this document, *uniform sampling* is used to create a sample and *one single circle* with a radius of 5 is used to compute local variables.

@@

```{r}
## BCa nonparametric
# Largely based on the code given in https://gitlab.com/scottkosty/bootstrap/-/blob/master/R/bcanon.R
# Function explained in Efron and Tibshirani (1993)
# Adapted for our particular problem
bcanon <- function(df_init,est_init,est_boot_val,p,...,alpha =
                     c(.025,.975)) { 
    # n <- nrow(x)
    # a <- mapply(theta, x[, 1], x[, 2])
    # Estimated total thus obtained from the initial sample
    # thetahat <- sum(a/p)

    nboot <- nrow(est_boot_val)
    # thetastar <- c()
    # for (c in 1:B) {
    #   a <- mapply(theta, est_boot[, (2*c)-1], est_boot[, 2*c])
    #   thetastar <- append(thetastar, sum(a/p))
    # }
    thetastar <- as.data.frame(mapply(sort, est_boot_val))

@@

    # z0 <- qnorm(sum(thetastar<thetahat)/nboot)

    u <- data.frame(x = numeric(), y = numeric())
    for(i in 1:n){
        x_i <- df_init[-i,]
        # a <- c()
        # for (j in 1:(n-1)) {
        #   a <- append(a, theta(x_i[j, 1], x_i[j, 2]))
        # }
        u <- rbind(u, c(sum(x_i[3]/p), sum(x_i[4]/p)))
    }
    u <- cbind(u, mapply(function(x,y){x/y}, u[2], u[1]))
    uu <- as.data.frame( mapply(function(some_vec){mean(some_vec)-some_vec}, u) )
    # uu <- mean(u)-u
    acc <- mapply(function(some_vec){sum(some_vec**3)/(6*(sum(some_vec**2))^1.5)}, uu)
    # acc <- sum(uu*uu*uu)/(6*(sum(uu*uu))^1.5)

@@

    tt <- as.data.frame( mapply(function(z0, acc){pnorm(z0+ (z0+zalpha)/(1-acc*(z0+zalpha)))}, z0, acc) )
    # tt <- pnorm(z0+ (z0+zalpha)/(1-acc*(z0+zalpha)))

    confpoints <- as.data.frame( mapply(function(tt, thetastar){quantile(x=thetastar,probs=tt,type=1)}, tt, thetastar) )
    # confpoints <- quantile(x=thetastar,probs=tt,type=1)
    # confpoints <- quantile(x=thetastar,probs=tt,type=1)
    rownames(confpoints) <- NULL
    # confpoints <- cbind(alpha,confpoints)
    # dimnames(confpoints)[[2]] <- c("alpha","bca point")
    return(confpoints)
}
```

@@

>>>>

In this document, \textbf{uniform sampling} is used to create a sample and \textbf{one single circle} with a radius of 5 is used to compute local variables.

@@

```{r}
## BCa nonparametric
# Largely based on the code given in https://gitlab.com/scottkosty/bootstrap/-/blob/master/R/bcanon.R
# Function explained in Efron and Tibshirani (1993)
# Adapted for our particular problem
bcanon <- function(df_init,est_init,est_boot_val,p,...,alpha =
                     c(.025,.975)) { 
    # df_init: initial sample
    # est_init: estimation made thanks to the initial sample
    # est_boot_val: estimations made thanks to bootstrap samples
    # p: inclusion density

    nboot <- nrow(est_boot_val)
    thetastar <- as.data.frame(mapply(sort, est_boot_val))

@@

    u <- data.frame(x = numeric(), y = numeric())
    for(i in 1:n){
        x_i <- df_init[-i,]
        u <- rbind(u, c(sum(x_i[3]/p), sum(x_i[4]/p)))
    }
    u <- cbind(u, mapply(function(x,y){x/y}, u[2], u[1]))
    uu <- as.data.frame( mapply(function(some_vec){mean(some_vec)-some_vec}, u) )
    acc <- mapply(function(some_vec){sum(some_vec**3)/(6*(sum(some_vec**2))^1.5)}, uu)

@@

    tt <- as.data.frame( mapply(function(z0, acc){pnorm(z0+ (z0+zalpha)/(1-acc*(z0+zalpha)))}, z0, acc) )

    confpoints <- as.data.frame( mapply(function(tt, thetastar){quantile(x=thetastar,probs=tt,type=1)}, tt, thetastar) )
    rownames(confpoints) <- NULL
    return(confpoints)
}
```

@@

```{r}
TC_bca <- coverage_rate(4)
cat("Concerning the BCa approach, the coverage rates are the following: \n - for the number of trees: ", 
    TC_bca[1,1], "\n - for the volume of trees: ", TC_bca[2,1], "\n - for the ratio volume / number of trees: ", TC_bca[3,1],
    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
    TC_bca[1,2], "\n - for the volume of trees: ", TC_bca[2,2], "\n - for the ratio volume / number of trees: ", TC_bca[3,2],
    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
    TC_bca[1,3], "\n - for the volume of trees: ", TC_bca[2,3], "\n - for the ratio volume / number of trees: ", TC_bca[3,3],
    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
    TC_bca[1,4], "\n - for the volume of trees: ", TC_bca[2,4], "\n - for the ratio volume / number of trees: ", TC_bca[3,4])
```
